% Created 2017-02-08 Wed 12:54
% Intended LaTeX compiler: pdflatex
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Tedward Erker}
\date{\today}
\title{Tedward Erker}
\hypersetup{
 pdfauthor={Tedward Erker},
 pdftitle={Tedward Erker},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 24.5.1 (Org mode 9.0.1)},
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents


\section*{Research}
\label{sec:org5f7b566}
I like to call myself an urban ecologist.  I seek to understand the interaction between humans and the
environment in the places where most of us live: cities.  More
specifically, I'm interested in how urban forests affect urban
climate, building energy use, and carbon emissions.  I use Madison, WI
as a case study.

I strive to make all my work fully reproducible using \href{https://www.gnu.org/software/emacs/tour/}{emacs}
\href{http://orgmode.org/}{org-mode}.  Also, I love brilliant data \href{https://d3js.org/}{visualizations} and want
to use them to communicate science.

\section*{Background}
\label{sec:org0acd7b7}
\begin{itemize}
\item Student - Washington University in St. Louis, 2006-10.
\begin{itemize}
\item founded student vegetable garden, The Burning Kumquat
\item took junior year off to work on farms in Kentucky and Vermont and
to bike California coast
\item Summer research assistant, Tyson Research Center.  Identify over
100 species of plants.
\item Graduated summa cum laude with degree in Environmental Studies-
biology/ecology track.  Advisor: Tiffany Knight
\end{itemize}
\item Teacher - Biology and Chemistry at Confluence Prep Academy, 2010-2012
\begin{itemize}
\item Taught over 120 students in six classes daily.  As first year
teacher, developed chemistry curriculum for new charter school
integrating College Readiness Standards with Missouri Science
Standards.  Cross-country coach.
\end{itemize}
\item Tree Care Worker - American Tree Experts and Urban Tree Alliance, 2013-2014
\begin{itemize}
\item Mostly dragged brush into chippers.  Also climber and certified pesticide
applicator, treated for a number of pests including the emerald
ash borer.
\end{itemize}
\item Teaching Assistant
\begin{itemize}
\item Forest Ecology, Fall 2013, with Prof. Tom Gower
\item Living With Wildlife, Spring 2014 with Prof. Stan Temple
\item Forest Ecology, Fall 2014 with Prof. Phil Townsend
\item Statistical Methods for Bioscience II, Spring 2015 with Prof. Murray Clayton
\end{itemize}
\item Student - University of Wisconsin-Madison, 2013-2018 (expected)
\begin{itemize}
\item MS degree in \href{https://www.stat.wisc.edu/masters-biometry}{Biometry}, department of statistics,
advisor: Jun Zhu
\item PhD degree in \href{http://forestandwildlifeecology.wisc.edu/sites/default/files/ForestryPhDHandbook1162.pdf}{Forestry}, department of Forest and Wildlife Ecology,
advisor: Phil Townsend.  Committee Members: Eric Kruger, Annemarie
Schneider, Chris Kucharik
\end{itemize}
\end{itemize}

\section*{\href{blog.html}{Blog}}
\label{sec:org2245daf}

\href{blog.html}{my notes on things}



\section*{Grants and Awards}
\label{sec:org26c79c4}
\begin{itemize}
\item George Kress Award for Outstanding Contribution of a Forestry Graduate
Student, 2016, \$1000
\item \href{https://www.nasa.gov/multimedia/imagegallery/iotd.html}{NASA} Earth and Space Science \href{data/NESSF15_selections.pdf}{Fellowship}, 2015-2018, \$90,000
\item Outstanding Overall Achievement in Environmental Studies (highest award in major), Washington University in St. Louis 2010.
\item Cool Science Image contest winner, ADD MORE HERE. \$100
\end{itemize}
\section*{Grants and Awards}
\label{sec:orgb8a4943}
\begin{itemize}
\item George Kress Award for Outstanding Contribution of a Forestry Graduate
Student, 2016, \$1000
\item \href{https://www.nasa.gov/multimedia/imagegallery/iotd.html}{NASA} Earth and Space Science \href{data/NESSF15_selections.pdf}{Fellowship}, 2015-2018, \$90,000
\item Outstanding Overall Achievement in Environmental Studies (highest award in major), Washington University in St. Louis 2010.
\item Cool Science Image contest winner, ADD MORE HERE. \$100
\end{itemize}
\section*{Teaching and Learning}
\label{sec:org0763903}

While teaching high school, I experienced the joy and challenges of
student learning.  I developed the skills that made me a successful
teaching assistant, and that I hope to continue to develop in higher education.

It's truly satisfying to help students grow and build confidence in their
skills.  I am excited to be pursuing a career where I can teach about
topics that inspire me, and that I hope will inspire my students.

\section*{Presentations}
\label{sec:org9c1c215}
\begin{itemize}
\item \href{presentations/SAF_20161105/saf_presentation.html}{Mapping Urban Tree Canopy of Wisconsin (Society of American Foresters National Convention)}
\end{itemize}

\section*{Contact}
\label{sec:org3950779}

erker wisc.edu

I limit my presence on social media to prevent distraction, but that
makes it harder to stay in touch.  If you are an old friend or former
student who found this website, please email me.  I'd love to catch up
and get a cup of joe if you're in town.
\end{document}