% Created 2018-06-28 Thu 12:26
% Intended LaTeX compiler: pdflatex
\documentclass[11pt, sans]{moderncv}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[scale=0.75]{geometry}
\name{Tedward}{Erker}
\address{Madison, WI}
\phone[mobile]{(314)~324~6079}
\email{tedward.erker@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{stat.wisc.edu/~erker/}                         % optional, remove / comment the line if not wanted
\social[github]{tedwarderker}                              % optional, remove / comment the line if not wanted
\title{title}                               % optional, remove / comment the line if not wanted
\date{\today}
\title{~}
\hypersetup{
 pdfauthor={Tedward Erker},
 pdftitle={~},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 25.1.1 (Org mode 9.1.7)},
 pdflang={English}}
\begin{document}

\maketitle
\section*{Experience}
\label{sec:org01676c3}
\cventry{2015--Present}{Research Assistant}{UW-Madison}{}{}{%
\begin{itemize}
\item Map Urban Forests of Wisconsin
\begin{itemize}
\item Tested 3 machine learning algorithms to classify terabytes of imagery
\item Processed imagery in parallel at UW's Center for High Throughput Computing
\item Geospatial analysis in R and image segmentation in python.
\end{itemize}
\item Carbon Budget of Urban Forest
\begin{itemize}
\item Assessed impact of tree canopy on residential building energy use
and carbon emissions of \textasciitilde{}30,000 Madison homes.
\end{itemize}
\item Canopy Foliar Trait Mapping with \href{https://aviris-ng.jpl.nasa.gov/}{Imaging Spectroscopy}.
\begin{itemize}
\item Applied partial least squares regression models to predict foliar
canopy traits (e.g.  nitrogen content) from \href{https://aviris-ng.jpl.nasa.gov/}{imaging spectroscopy}
data
\item Explored anthropogenic and environmental drivers of trait variation
across Madison, WI.
\end{itemize}
\end{itemize}
}

\cventry{2013--2015}{Teaching Assistant}{UW-Madison}{}{}{%
\begin{itemize}
\item Statistical Methods for Bioscience II, Spring 2015
\begin{itemize}
\item Led 2 weekly discussion groups, graded homework and exams for
  this graduate-level course largely covering multiple linear and
logistic regression
\end{itemize}
\item Forest Ecology, Fall 2013 and Fall 2014
\item Living With Wildlife, Spring 2014
\end{itemize}
}

\cventry{2010--2012}{Chemistry and Biology Teacher}{Confluence Prep Academy}{St. Louis}{}{
\begin{itemize}
\item Educated over 120 students in six classes daily.
\item As first year teacher, developed chemistry curriculum for new charter school integrating College Readiness Standards with Missouri Science Standards.
\end{itemize}
}

\cventry{2010--2012}{Corps Member}{Teach For America}{Chicago \& St. Louis}{}{
}

\section*{Education}
\label{sec:orga17cbfa}
\cventry{2013--Present}{Ph.D.}{University of Wisconsin--Madison}{}{\textit{3.929}}{Forestry, Department of Forest and Wildlife Ecology}
\cventry{2013--Present}{M.S.}{University of Wisconsin--Madison}{}{}{\href{https://www.stat.wisc.edu/masters-biometry}{Biometry}, Department of Statistics}
\cventry{2006--2010}{B.A.}{Washington University in St. Louis}{}{\textit{3.83}}{Environmental Studies--Ecology/Biology, Summa Cum Laude}

\section*{Relevant graduate coursework}
\label{sec:orge840fc0}
\cvlistdoubleitem{Tools for Reproducible Research}{Advanced Data Analysis with R}
\cvlistdoubleitem{Statistical Methods-Spatial Data}{Multilevel Models}
\cvlistdoubleitem{Intro Mathematical Statistics I \& II}{Statistical Meth. for Bioscience I \& II}
\cvlistdoubleitem{Teaching Statistics}{Statistical Consulting}

\section*{Skills}
\label{sec:org9accccc}
\cvitemwithcomment{Statistical Analysis}{}{GLMs, GAMs, multilevel models, shrinkage and dimension reduction, tree-based methods, dependent data in R and some Stan}
\cvitemwithcomment{Data Display}{}{Daily use of grammar of graphics in R's ggplot2}
\cvitemwithcomment{Writing}{}{1 scientific paper in review; over \$150,00 in proposals}
\cvitemwithcomment{Presenting}{}{2 scientific posters, 1 academic presentation, 4 years of teaching}
\cvitemwithcomment{Computing}{}{R, python, webscraping, emacs org mode, unix command line, version control (git)}
\cvitemwithcomment{Mentoring}{}{2 undergraduate research assistants, 4 years of teaching}

\section*{Awards, Grants, and Fellowships}
\label{sec:org9b56e2d}
\cvitemwithcomment{
Jan 2018
}{
\href{http://mc-stan.org/events/}{Stan Conference} Scholarship
}{}
\cvitemwithcomment{
2015-2018
}{
NASA Earth and Space Science \href{https://nspires.nasaprs.com/external/viewrepositorydocument/cmdocumentid=459947/solicitationId=\%7BB6CDCEA6-8EDD-A48A-FAF8-E588F66661C3\%7D/viewSolicitationDocument=1/NESSF15\%20selections.pdf}{Fellowship}
}{
\$105,000
}


\cvitemwithcomment{}{}{}
\cvitemwithcomment{}{}{}
\cvitemwithcomment{}{}{}
\cvitemwithcomment{}{}{}
\cvitemwithcomment{}{}{}
\cvitemwithcomment{}{}{}



\subsection*{Jan 2018}
\label{sec:org380a908}
\href{http://mc-stan.org/events/}{Stan Conference 2018} Scholarship

\subsection*{2015-2018}
\label{sec:orgca13e95}
NASA Earth and Space Science \href{https://nspires.nasaprs.com/external/viewrepositorydocument/cmdocumentid=459947/solicitationId=\%7BB6CDCEA6-8EDD-A48A-FAF8-E588F66661C3\%7D/viewSolicitationDocument=1/NESSF15\%20selections.pdf}{Fellowship}\\
\$105,000

\subsection*{Sep 2016}
\label{sec:org4a47595}
Mapping Wisconsin's Urban Tree Canopy (co-author), Wisconsin
Department of Natural Resources\\
\$50,000

\subsection*{Oct 2016}
\label{sec:org7eefa44}
\href{https://kb.wisc.edu/russell/page.php?id=65402}{George Kress Award} for Outstanding Contribution of a Forestry Graduate
Student \\
\$1,000

\subsection*{May 2016}
\label{sec:org6c84b79}
Travel Award, UW-Madison Department of Forest and Wildlife Ecology\\

\subsection*{Mar 2016}
\label{sec:org8dc2483}
\href{http://news.wisc.edu/cool-science-images-2016/\#\&gid=1\&pid=10}{Cool Science Image contest winner}, "Madison Lakes" \\

\subsection*{May  2010}
\label{sec:org0e41915}
\href{http://enst.wustl.edu/program/awards}{Outstanding Overall Achievement in Environmental Studies} (highest
award in major), Washington University in St. Louis

\subsection*{Jun 2008}
\label{sec:org83b5d93}
\href{https://tyson.wustl.edu/2008}{Tyson Research Center Summer Undergraduate Research Fellowship} \\
 \$3,750

\section*{Presentations}
\label{sec:org904cb03}
\subsection*{November 2016}
\label{sec:org0da9e2d}
\textbf{\href{http://pages.stat.wisc.edu/\~erker/Presentations/SAF\_20161105/saf\_presentation.html}{Mapping Urban Tree Canopy of Wisconsin}}

Society of American Foresters National Convention. Madison, WI.
\section*{Posters}
\label{sec:orge6c083e}
\subsection*{April 2018}
\label{sec:org779306b}
\textbf{\href{http://pages.stat.wisc.edu/\~erker/Posters/NASA\_poster\_2018.jpg}{Functional and Species Diversity of Trees in Urban Streets}}

NASA Biodiversity and Ecological Forecasting Team Meeting in
Washington, D.C.
\subsection*{May 2016}
\label{sec:org1001e99}
\textbf{\href{http://pages.stat.wisc.edu/\~erker/Posters/NASA\_poster\_2016.jp2}{How Does Structural and Functional Diversity of the Urban Forest
Affect the Urban Heat Island and Building Energy Use in Madison, WI?}}

NASA Biodiversity and Ecological Forecasting Team Meeting in Silver Springs, MD.
\section*{Teaching Experience}
\label{sec:org780ee20}
\subsection*{Spring 2015}
\label{sec:orgadc2331}
\textbf{Statistical Methods for Bioscience II Teaching Assistant}

Led 2 weekly discussion groups, graded homework and exams for this
graduate-level course. Prof. Murray Clayton.
;
\subsection*{Fall 2013 and Fall 2014}
\label{sec:org5afdb77}
\textbf{Forest Ecology Teaching Assistant}

Redesigned, created and independently implemented lab lessons in field and computer lab for \textasciitilde{}70
students.  Prof. Tom Gower (2013) and Prof. Phil Townsend (2014).

\subsection*{Spring 2014}
\label{sec:org4be10c6}
\textbf{Living With Wildlife Teaching Assistant}

Graded journals and exams, assisted students during office hours.
Prof. Stan Temple.

\subsection*{August 2010 - May 2012}
\label{sec:org36ac48f}
\textbf{High School Chemistry and Biology Teacher}

Educated over 120 students in six classes daily. As first year
teacher, developed chemistry curriculum for new charter school
integrating College Readiness Standards with Missouri Science
Standards. Cross-country coach. \href{https://www.google.com/search?q=Confluence+Preparatory+Academy+St.+Louis\&oq=Confluence+Prep+Academy+St.+Louis\&aqs=chrome..69i57.7294j0j8\&sourceid=chrome\&ie=UTF-8\#q=Confluence+Prep+Academy+High+School+St.+Louis}{Confluence Preparatory Academy}. St. Louis, MO.

\subsection*{June 2010 - May 2012}
\label{sec:orgb2e15c3}
\textbf{\href{https://www.teachforamerica.org/}{Teach For America} Corps Member}

Selected from over 46,000 applicants nationwide to join the national
teacher corps of recent college graduates who commit two years to
teach in under-resourced public schools.  Chicago, IL \& St. Louis, MO.

\section*{Mentoring}
\label{sec:org4af550a}

My undergraduate mentees research a topic, collect new data, perform statistical
analyses, and write final papers to complete small research projects.  They
create posters or presentations to share their work.

\subsection*{Fall 2017}
\label{sec:orgf34eeb7}
\textbf{Cheyenne Brandt}

Undergraduate Research Project: Effect of Leaf Area and Tree Canopy on the Urban
Heat Island of Madison, WI.

\subsection*{Fall 2015}
\label{sec:org43fb804}
\textbf{Bobby Shepherd}

Undergraduate Research Project: Investigating the influence of the
urban heat island on autumn phenology of Norway Maple (\emph{Acer
platanoides}) with smartphone hemispherical photos.
\section*{Relevant Work Experience}
\label{sec:org5a67348}

\subsection*{August 2013 - December 2014}
\label{sec:org0b2f305}
\textbf{Arborist}

Worked part time as ground crew, hauling brush and aiding climber.
Developed online Wisconsin tree species identification application.
\href{http://www.urbantreealliance.org/}{Urban Tree Alliance}, Non-profit. Madison, WI.

\subsection*{February 2013 - August 2013}
\label{sec:orge1cb924}
\textbf{Arborist}

Performed ground crew work, climbed, and as certified pesticide
applicator treated for a number of pests including the emerald ash
borer. \href{http://atetreecare.com/}{American Tree Experts}.  New Berlin, WI

\subsection*{March 2007 - May 2010}
\label{sec:org07abbd5}
\textbf{Greenhouse Assistant}

Water, transplant, propagate plants; maintain greenhouse. Work-Study
at \href{http://biology4.wustl.edu/greenhouse/index.html}{Washington University Plant Research Facility}. St. Louis, MO.

\subsection*{April - August 2009}
\label{sec:orgff1e200}
\textbf{Farm Education Intern and Farmer}

Organized and guided trips of 16-40 students at farm and wilderness
education center. Managed 3⁄4 acre garden and cared for sheep, goats,
chickens, pigs, and cows as part of farm team.  \href{https://farmandwilderness.org/}{Farm And Wilderness
Summer Camps}. Plymouth, VT.

\subsection*{May - August 2008}
\label{sec:org016186d}
\textbf{Research Assistant}

Sampled vegetation, identified over 100 plant species as part of study
to explore phylogenic relationships in invasiveness.  \href{https://tyson.wustl.edu/2008}{Tyson Research
Center}. Eureka, MO.
\section*{Professional Affiliations}
\label{sec:orga776f93}
Society of American Foresters, 2016--Present

\section*{Languages}
\label{sec:org67e6d84}
Spoken: English, Spanish

Computing: R

\section*{Service to the Department and University}
\label{sec:orgeb2f6ad}
\subsection*{Oct 2015 - Present}
\label{sec:org3b689e7}
\textbf{Graduate Student Representative, Department of Forest and Wildlife
Ecology}
\subsection*{Jul 2017}
\label{sec:org88f903c}
\textbf{Software Carpentry Volunteer}
\section*{Service to Community}
\label{sec:org625c2b3}
\subsection*{Fall 2014 and Fall 2015}
\label{sec:org9829d20}
\textbf{Guest Lab Instructor, Sustainability by the Numbers, Shabazz High School}

\subsection*{Fall 2017}
\label{sec:org5904596}
\textbf{Guest Lab Instructor, AP Environmental Studies, East High School}


\section*{Graduate Coursework}
\label{sec:org414590e}
\begin{center}
\begin{tabular}{lllrl}
Semester & Code & Course & Credits & Grade\\
\hline
F 2013 & F\&W ECOL 309 & Diseases of Trees and Shrubs & 3 & A\\
 & F\&W ECOL 415 & Tree Physiology & 3 & A\\
 & HORT 571 & Statistical Methods for Bioscience I & 4 & A\\
S 2014 & PL PATH 800 & Inquiry-Based Biology Teaching & 1 & A\\
 & STAT 692 & Intermediate Data Analysis with R & 1 & A\\
 & F\&W ECOL 410 & Principles of Silviculture & audit & S\\
 & STAT 572 & Statistical Methods for Bioscience II & 4 & A\\
 & PL PATH 801 & Teaching Biology: Special Topics & 1 & A\\
 & STAT 692 & Advanced Data Analysis with R & 1 & A\\
Su 2014 & MATH 234 & Calculus--Functions of Variables & 4 & S\\
F 2014 & F\&W ECOL 875 & Field Methods in Remote Sensing & 1 & A\\
 & SOIL SCI 532 & Environmental Biophysics & 3 & A\\
 & STAT 311 & Intro Mathematical Statistics I & 3 & A\\
S 2015 & BMI 826 & Tools for Reproducible Research & 1 & A\\
 & ENVIR ST 556 & Remote Sensing Digital Image Processing & 3 & A\\
 & STAT 312 & Intro Mathematical Statistics II & 3 & AB\\
 & STAT 692 & Teaching Statistics & 1 & A\\
Su 2015 & STAT 699 & Statistical Consulting & 3 & A\\
F 2015 & STAT 575 & Statistical Methods-Spatial Data & 3 & AB\\
S 2016 & STAT 679 & Multilevel Models & 3 & A\\
S 2017 & ZOOLOGY 725 & Ecosystem Concepts & 3 & \\
\end{tabular}
\end{center}
\end{document}